Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience

### 2016-05-26 paper.tex
Adds rules to build graphs from previous results in Makefile Adds directions to access previous results in README Adds create/delete overhead graphs and first pass at discussion of overhead test

\section{Evaluation}
In order to properly capture the relevant performance characteristics of loop devices as compared to the native filesystem, the evaluation of the library consists of standard micro-benchmarks which test throughput performance.

@@

Each micro-benchmark test ran for twenty iterations then created a nested loop device within the current device. This process was completed twenty times resulting in a loop device nested within twenty other loop devices. This nesting shows a reduction in device performance the deeper the device is nested. Though nesting a loop device within another is feasible in terms of performance, it is not the expected behavior of a workflow. Regardless, we demonstrate that an entire workflow can run within a storage container and still perform reasonably. The aim of these micro-benchmarks was to demonstrate that a loop device does not experience a steep performance decline in order to provide a resource guarantee for a workflow task. We have provided the first ten iterations of the test as they are most pertinent.

@@

Availability of the experiment is an important consideration for reproducibility. We have provided the source code, which is freely available on GitHub at {\tt{https://github.com/cooperative-computing-lab/disk-alloc-experiment}}. Within this git repository we have included a convenient Makefile which makes running the experiment quite simple. This Makefile downloads all the dependent code for the experiment except some software listed in the {\tt{README}} located in the repository as well as runs the specified tests, generates graphs from the test data, and compiles this paper. We chose to provide this depth of content because reproducibility and availability are high priorities with respect to this technical report.

@@

\section{Conclusion}
Though resource constraint does not have much support, we present a novel method of constraining the storage usage of a batch job task through the use of loop devices. Loop devices, as opposed to a sentinel process, provide an instantaneous handling of storage exhaustion. This passive method of constraint keeps a task within its requested storage. This in turns prevents the task from using up enough space to affect the availability of the host machine for future work. We have shown that loop devices provide these benefits with a reasonable performance guarantee.

\newpage
\newcommand{\cimage}[1]{$\vcenter{\hbox{\includegraphics[width=0.3\textwidth]{#1}}}$}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{read_ext2_2GB.pdf} & \cimage{write_ext2_2GB.pdf} & \cimage{meta_ext2_2GB.pdf}\\
ext3 & \cimage{read_ext3_2GB.pdf} & \cimage{write_ext3_2GB.pdf} & \cimage{meta_ext3_2GB.pdf}\\
ext4 & \cimage{read_ext4_2GB.pdf} & \cimage{write_ext4_2GB.pdf} & \cimage{meta_ext4_2GB.pdf}\\
\end{tabular}
\label{fig:2gb}
\caption{Loop Device Performance with 2GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{read_ext2_4GB.pdf} & \cimage{write_ext2_4GB.pdf} & \cimage{meta_ext2_4GB.pdf}\\
ext3 & \cimage{read_ext3_4GB.pdf} & \cimage{write_ext3_4GB.pdf} & \cimage{meta_ext3_4GB.pdf}\\
ext4 & \cimage{read_ext4_4GB.pdf} & \cimage{write_ext4_4GB.pdf} & \cimage{meta_ext4_4GB.pdf}\\
\end{tabular}
\label{fig:4gb}
\caption{Loop Device Performance with 4GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{read_ext2_8GB.pdf} & \cimage{write_ext2_8GB.pdf} & \cimage{meta_ext2_8GB.pdf}\\
ext3 & \cimage{read_ext3_8GB.pdf} & \cimage{write_ext3_8GB.pdf} & \cimage{meta_ext3_8GB.pdf}\\
ext4 & \cimage{read_ext4_8GB.pdf} & \cimage{write_ext4_8GB.pdf} & \cimage{meta_ext4_8GB.pdf}\\
\end{tabular}
\label{fig:8gb}
\caption{Loop Device Performance with 8GB Allocations}
\end{figure*}

>>>>

\section{Evaluation}
In order to properly capture the relevant performance characteristics of loop devices as compared to the native filesystem, the evaluation of the library consists of standard micro-benchmarks which test throughput performance as well as overhead of loop device instantiation and deletion.

@@

Each micro-benchmark test ran for twenty iterations then created a nested loop device within the current device. This process was completed twenty times resulting in a loop device nested within twenty other loop devices. This nesting shows a reduction in device performance the deeper the device is nested. Though nesting a loop device within another is feasible in terms of performance, it is not the expected behavior of a workflow. Regardless, we demonstrate that an entire workflow can run within a storage container and still perform reasonably. The aim of these micro-benchmarks was to demonstrate that a loop device does not experience a steep performance decline in order to provide a resource guarantee for a workflow task. We have provided the first ten nest depths of the test as they are most pertinent.

We also measured the overhead associated with the creation and deletion of loop devices. Much like the throughput performance tests, each test ran for twenty iterations. However, we did not take into account nesting for these two micro-benchmarks. We measured the time to create a loop device sandbox starting at a size of 1MB and increasing in logarithmic scale to 8GB. We also timed how long it took to delete the loop device sandbox.

@@

Availability of the experiment is an important consideration for reproducibility. We have provided the source code, which is freely available on GitHub at {\tt{https://github.com/cooperative-computing-lab/disk-alloc-experiment}}. Within this git repository we have included the data collected for this technical report and a convenient Makefile which makes running the experiment quite simple. This Makefile downloads all the dependent code for the experiment except some software listed in the {\tt{README}} located in the repository as well as runs the specified tests, generates graphs from the test data, and compiles this paper. We chose to provide this depth of content because reproducibility and availability are high priorities with respect to this technical report.

@@

\section{Conclusion}
Though resource constraint does not have much support, we present a novel method of constraining the storage usage of a batch job task through the use of loop devices. Loop devices, as opposed to a sentinel process, provide an instantaneous handling of storage exhaustion. This passive method of constraint keeps a task within its requested storage while also guaranteeing resources to it. This in turns prevents the task from using up enough space to affect the availability of the host machine for future work. We have shown that loop devices provide these benefits with a reasonable performance guarantee.

\newcommand{\cimage}[1]{$\vcenter{\hbox{\includegraphics[width=0.3\textwidth]{#1}}}$}

\begin{figure*}[t]
\begin{tabular}{ccc}
ext2 & \cimage{./previous_results/create_ext2.pdf} & \cimage{./previous_results/delete_ext2.pdf}\\
ext3 & \cimage{./previous_results/create_ext3.pdf} & \cimage{./previous_results/delete_ext3.pdf}\\
ext4 & \cimage{./previous_results/create_ext4.pdf} & \cimage{./previous_results/delete_ext4.pdf}\\
\end{tabular}
\label{fig:create}
\caption{Loop Device Creation/Deletion Overhead}
\end{figure*}

\newpage
\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_2GB.pdf} & \cimage{./previous_results/write_ext2_2GB.pdf} & \cimage{./previous_results/meta_ext2_2GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_2GB.pdf} & \cimage{./previous_results/write_ext3_2GB.pdf} & \cimage{./previous_results/meta_ext3_2GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_2GB.pdf} & \cimage{./previous_results/write_ext4_2GB.pdf} & \cimage{./previous_results/meta_ext4_2GB.pdf}\\
\end{tabular}
\label{fig:2gb}
\caption{Loop Device Performance with 2GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_4GB.pdf} & \cimage{./previous_results/write_ext2_4GB.pdf} & \cimage{./previous_results/meta_ext2_4GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_4GB.pdf} & \cimage{./previous_results/write_ext3_4GB.pdf} & \cimage{./previous_results/meta_ext3_4GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_4GB.pdf} & \cimage{./previous_results/write_ext4_4GB.pdf} & \cimage{./previous_results/meta_ext4_4GB.pdf}\\
\end{tabular}
\label{fig:4gb}
\caption{Loop Device Performance with 4GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_8GB.pdf} & \cimage{./previous_results/write_ext2_8GB.pdf} & \cimage{./previous_results/meta_ext2_8GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_8GB.pdf} & \cimage{./previous_results/write_ext3_8GB.pdf} & \cimage{./previous_results/meta_ext3_8GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_8GB.pdf} & \cimage{./previous_results/write_ext4_8GB.pdf} & \cimage{./previous_results/meta_ext4_8GB.pdf}\\
\end{tabular}
\label{fig:8gb}
\caption{Loop Device Performance with 8GB Allocations}
\end{figure*}
